# The Standard data
# -----------------------------------------------------
## Load the .csv and exclude so id vars

```{r}
datS <- read.csv("http://www.qogdata.pol.gu.se/data/qog_std_ts_15may13.csv",  sep = ";")
datSmot <- datS[,c(-1,-4,-5,-6,-7,-8,-9)]
```

## Subset the data for smoother rendering in browser
### Only the years after 1990
```{r}
datSmot2 <- datSmot[datSmot$year >= 2000, ]
```

## Generate the Motion Chart and save it
```{r}
library(googleVis)
motionStandard <- gvisMotionChart(datSmot2, idvar="cname",
                              timevar="year",
                              xvar="mad_gdppc",
                              yvar="undp_hdi",
                              sizevar="mad_pop",
                              options=list(height=900, width=1100))
## Save
print(motionStandard, file="motionStandard.html")
```

- (Click here to browse the motion chart)[motionStandard.html]


# The social policy data

```{r}
datSP <- read.csv("http://www.qogdata.pol.gu.se/data/qog_soc_tsl_4apr12.csv",  sep = ";")
datSPmot <- datSP[,c(-1,-4,-5,-6,-7,-8)]
```


## Subset the data for smoother rendering in browser
### Only the years after 1990
```{r}
datSPmot2 <- datSPmot[datSPmot$year >= 2000, ]
```

## Generate the Motion Chart and save it
```{r}
library(googleVis)
motionSocialPolicy <- gvisMotionChart(datSPmot2, idvar="cname",
                                      timevar="year",
                                      xvar="wdi_gdp",
                                      yvar="wdi_gini",
                                      sizevar="wdi_pop",
                                      options=list(height=900, width=1100))
## Save
print(motionSocialPolicy, file="motionSocialPolicy.html")
```

- (Click here to browse the motion chart)[motionSocialPolicy.html]