# Make plots

# All the countries

## Load the .csv and exclude so id vars

```{r, cache=TRUE}
datS <- read.csv("http://www.qogdata.pol.gu.se/data/qog_std_ts_15may13.csv",  sep = ";")
datSmot <- datS[,c(-1,-4,-5,-6,-7,-8,-9)]

datSP <- read.csv("http://www.qogdata.pol.gu.se/data/qog_soc_tsl_4apr12.csv",  sep = ";")
datSPmot <- datSP[,c(-1,-4,-5,-6,-7,-8)]
```


## Generate the Motion Chart and save it
```{r, cache=TRUE}
datSmot2 <- datSmot[datSmot$year >= 2000, ]
library(googleVis)
motionStandard <- gvisMotionChart(datSmot2, idvar="cname",
                              timevar="year",
                              xvar="mad_gdppc",
                              yvar="undp_hdi",
                              colorvar="fh_pr",
                              sizevar="mad_pop",
                              options=list(height=900, width=1100))
## Save
print(motionStandard, file="motionStandard.html")
## plot
datSPmot2 <- datSmot[datSPmot$year >= 2000, ]
motionSocialPolicy <- gvisMotionChart(datSPmot2, idvar="cname",
                                      timevar="year",
                                      xvar="wdi_gdp",
                                      yvar="wdi_gini",
                                      colorvar="fh_pr",
                                      sizevar="wdi_pop",
                                      options=list(height=900, width=1100))
## Save
print(motionSocialPolicy, file="motionSocialPolicy.html")
```


- [Click here to browse the motion chart](http://muuankarski.github.io/QogGVis/motionStandard.html)
- [Click here to browse the motion chart](http://muuankarski.github.io/QogGVis/motionSocialPolicy.html)

# Post socialist countries from 1990

## Generate the Motion Chart and save it
```{r, cache=TRUE}
clist <-  c('Czech Republic','Estonia','Hungary',
            'Bulgaria','Latvia','Lithuania',
            'Poland','Slovakia','Slovenia',
            'Romania','Albania','Bosnia',
            'Bulgaria','Croatia','Macedonia',
            'Montenegro','Kosovo','Serbia',
            'Armenia','Azerbaijan','Belarus',
            'Georgia','Kazakhstan','Kyrgyzstan',
            'Moldova','Mongolia','Russia',
            'Tajikistan','Ukraine','Uzbekistan')

datSmot2 <- datSmot[datSmot$year >= 1990, ]
datSmot3 <- datSmot2[datSmot2$cname %in% clist, ]
library(googleVis)
motionStandardPostS <- gvisMotionChart(datSmot3, idvar="cname",
                              timevar="year",
                              xvar="mad_gdppc",
                              yvar="undp_hdi",
                              sizevar="mad_pop",
                              colorvar="fh_pr",
                              options=list(height=900, width=1100))
## Save
print(motionStandardPostS, file="motionStandardPostS.html")
## plot
datSPmot2 <- datSPmot[datSPmot$year >= 1990, ]
datSPmot3 <- datSPmot2[datSPmot2$cname %in% clist, ]
motionSocialPolicyPostS <- gvisMotionChart(datSPmot3, idvar="cname",
                                      timevar="year",
                                      xvar="wdi_gdp",
                                      yvar="wdi_gini",
                                      sizevar="wdi_pop",
                                      colorvar="fh_pr",
                                      options=list(height=900, width=1100))
## Save
print(motionSocialPolicyPostS, file="motionSocialPolicyPostS.html")
```


- [Click here to browse the motion chart](http://muuankarski.github.io/QogGVis/motionStandardPostS.html)
- [Click here to browse the motion chart](http://muuankarski.github.io/QogGVis/motionSocialPolicyPostS.html)


# Eu countries from 1990

## Generate the Motion Chart and save it
```{r, cache=TRUE}
clistEu <- c("Austria","Belgium","Bulgaria","Cyprus",
              "Czech Republic","Denmark","Estonia","Finland",
              "France","Germany","Greece","Hungary","Iceland",
              "Ireland","Italy","Latvia","Lithuania",
              "Luxembourg","Malta","Netherlands",
              "Norway","Poland","Portugal","Romania",
              "Slovakia","Slovenia","Spain","Sweden",
              "Switzerland","United Kingdom")
datSmot2 <- datSmot[datSmot$year >= 1990, ]
datSmot3 <- datSmot2[datSmot2$cname %in% clistEu, ]
library(googleVis)
motionStandardEu <- gvisMotionChart(datSmot3, idvar="cname",
                              timevar="year",
                              xvar="mad_gdppc",
                              yvar="undp_hdi",
                              colorvar="fh_pr",
                              sizevar="mad_pop",
                              options=list(height=900, width=1100))
## Save
print(motionStandardEu, file="motionStandardEu.html")
## plot
datSPmot2 <- datSPmot[datSPmot$year >= 1990, ]
datSPmot3 <- datSPmot2[datSPmot2$cname %in% clistEu, ]
motionSocialPolicyEu <- gvisMotionChart(datSPmot3, idvar="cname",
                                      timevar="year",
                                      xvar="wdi_gdp",
                                      yvar="wdi_gini",
                                      colorvar="fh_pr",
                                      sizevar="wdi_pop",
                                      options=list(height=900, width=1100))
## Save
print(motionSocialPolicyEu, file="motionSocialPolicyEu.html")
```

- [Click here to browse the motion chart](http://muuankarski.github.io/QogGVis/motionStandardEu.html)
- [Click here to browse the motion chart](http://muuankarski.github.io/QogGVis/motionSocialPolicyEu.html)

# Exit/Entry selection from 1990

## Generate the Motion Chart and save it
```{r, cache=TRUE}
clistOlli <- c("Australia","Austria","Belgium",
             "Canada","Denmark ","Finland ",
             "France","Germany","Ireland",
             "Italy","Japan","Netherlands",
             "New Zealand","Norway","Sweden",
             "Switzerland","United Kingdom","United States")

# datSmot2 <- datSmot[datSmot$year >= 1990, ]
# datSmot3 <- datSmot2[datSmot2$cname %in% clistEu, ]
# library(googleVis)
# motionStandardEu <- gvisMotionChart(datSmot3, idvar="cname",
#                               timevar="year",
#                               xvar="mad_gdppc",
#                               yvar="undp_hdi",
#                               colorvar="fh_pr",
#                               sizevar="mad_pop",
#                               options=list(height=900, width=1100))
# ## Save
# print(motionStandardEu, file="motionStandardEu.html")
## plot
datSPmot2 <- datSPmot[datSPmot$year >= 1980, ]
datSPmot3 <- datSPmot2[datSPmot2$cname %in% clistOlli, ]
motionSocialPolicyExit <- gvisMotionChart(datSPmot3, idvar="cname",
                                      timevar="year",
                                      xvar="socx_hput",
                                      yvar="wdi_lifexp",
                                      colorvar="cname",
                                      sizevar="wdi_pop",
                                      options=list(height=900, width=1100))
## Save
print(motionSocialPolicyExit, file="motionSocialPolicyExit.html")
```

- [Click here to browse the motion chart](http://muuankarski.github.io/QogGVis/motionStandardEu.html)
- [Click here to browse the motion chart](http://muuankarski.github.io/QogGVis/motionSocialPolicyEu.html)
